% This file was converted from HTML to LaTeX with
% Tomasz Wegrzanowski's <maniek@beer.com> gnuhtml2latex program
% Version : 0.1
\documentclass{article}
\usepackage{hyperref}

\begin{document}
		\begin{centering}\subsection*{Course Information:}\end{centering}
		\begin{tabular}{ll}
				\textbf{Course:} Math 1205 &
				\textbf{Instructor:} Erich L Foster \\
				\textbf{Classroom:} RAND 116 & 
				\textbf{Office:} McBryde 461J \\
				\textbf{Meeting Time:} MWF 12:20-1:10PM &
				\textbf{Office Hours:} TTh 11-12:30PM \\
				\textbf{Section:} 18666
		\end{tabular} \\
			
			\subsubsection*{Text} 
			\emph{University Calculus}, 1st Edition, Haas-Weir-Thomas

			\subsubsection*{Prerequisites} 
			You must have one of the following: 
			\begin{itemize}
				\item   a grade of B or better in Math 1015/1016
				\item   two units of high school algebra, one unit of geometry,
					1/2 unit each of trigonometry and precalculus AND placement by
					the Mathematics Department
				\item   a passing grade in the Calculus Readiness Exam.
			\end{itemize} 
				
			\subsubsection*{Course Content} 
			We will cover the material listed on the course
			\href{http://www.emporium.vt.edu/math1205/resources/syllabus.html}{syllabus}.
			Any changes will be announced in class. Each student is responsible for
			taking weekly online
			\href{http://www.emporium.vt.edu/math1205/resources/quizzes}{quizzes} and
			completing assigned
			\href{http://www.math.vt.edu/people/erichlf/HWS11.html}{homework}.

			\subsubsection*{Course Format} 
			Lecture classes will meet on Mondays, Wednesdays and Fridays for 50
			minutes.  Class attendance will be taken and recorded. Written homework
			assignments will be collected at the beginning of class. See the
			Homework section below for more details. There will be 11 online
			quizzes. Each quiz contains 6 questions with the exception of Quiz 1
			which contains 12 questions.  Quiz 1 is a Trigonometry and Pre-Calculus
			review quiz and does not cover any material to be covered in class.
			Students are expected to have learned the material on Quiz 1 prior to
			taking Math 1205.
		
			\subsubsection*{Attendance} 
			Class attendance will be taken daily and kept for Mathematics Department
			records. Students are responsible for course materials and announcements
			covered in class.

			\subsubsection*{Tests} 
			There will be 3 common-time exams and a common-time final exam. The \href{http://www.emporium.vt.edu/math1205/resources/testinfo}{locations
			for the exams} will be announced on the Math 1205 web page.
			Typically, they will not be the same as our lecture class. \\ \\
			You must take tests on the specified date. If you have a Virginia Tech
			class that meets at the time scheduled for an exam, an alternative
			starting time for the exam later in the evening will be provided.  No
			makeup tests will be given.  Do NOT take this lightly. If it is to your
			benefit, your grade on the final exam will replace your lowest test
			grade. \\ \\
			The final exam is a required class meeting that will not be rescheduled
			for discretionary reasons, including conflicts with work schedules and
			with classes and exams at other colleges. 
			
			\subsubsection*{Homework}
			Homework assignments will be due at the beginning of class unless
			otherwise specified and are considered late after collection in class. No
			late work will be accepted, without valid excuse, i.e. illness or
			emergency. You are encouraged to work with other students in our class on
			the homework, but the work that you hand in must be your own. The Honor
			Code is in effect for all assignments. Written homework assignments are
			posted on the course web page by section. Tentative homework due dates are
			posted \href{http://www.math.vt.edu/people/erichlf/HWS11.html}{here}.
			At least one homework grade will be dropped. 
			
			\subsubsection*{Office Hours} 
			Office hours begin 20 January and end 05 May. Exam office hours will
			be given later. No office hours will be held during breaks.  If you can't
			make the scheduled office hours, then please check my \href{http://www.math.vt.edu/people/erichlf/}{website's calendar} to see
			other open times and then email me with a suggested time for an
			appointment. 
			
			\subsubsection*{Grading} 
			\begin{itemize}
				\item   Online Quizzes:	15\%
				\item   Homework:	20\%
				\item   Exams:	45\%(15\% each)
				\item   Final Exam:	20\%
			\end{itemize}
			A 90\% will guarantee an A-, 80\% a B-, 70\% a C-, 60\% a D-.
			Plus and minus grades will be assigned at my discretion.
			
			\subsubsection*{Honor System} 
			You must abide by the Virginia Tech Honor Code for all graded work.  \href{http://www.emporium.vt.edu/math1205/resources/honorpolicy.html}{See
			this webpage} for further information about your responsibilities.
			
			\subsubsection*{Classroom Courtesy} 
			You and your classmates are entitled to learn in an atmosphere of mutual
			respect, and freedom from distractions and disturbances. 
		
			
		 
			\subsubsection*{Important} 
			If you are not on the official class roll, you are not in the class.  It
			is your responsibility that you are properly enrolled in the class section
			you attend.  It is easy to verify.  For no foreseeable reason (computer
			and/or registrar personnel mistakes included) will you be allowed to stay
			in the wrong section.  Your work will not be graded.  Simply attending a
			section will NOT entitle you to be placed on its roll. \\ \\
			If you need adaptations or accommodations because of a disability, please
			make an appointment with me as soon as possible.
		
			
		 
			\subsubsection*{Important Dates} 
				\textbf{Last Day to Add Classes:} Monday, 28 January \\
				\textbf{Last Day to Drop Classes Without Grade Penalty:} Monday, 28
				February \\
				\textbf{Spring Break:} Monday, 07 March - Friday, March 11 \\
				\textbf{Last Day to Resign Without Grade Penalty:} Monday, 21 March \\
				\textbf{Deadline for undergraduates to request rescheduling of final
				examinations that conflict or constitute a third exam in 24 hours (See
				you Academic Dean):} Friday, 15 April \\
				\textbf{Thanksgiving Break:} Saturday, 20 November - Sunday, 28 November \\
				\textbf{Last Day to apply for Course Withdrawal:} Friday, 29 April \\ 
				\textbf{Classes end:} Wednesday, 04 May \\
				\textbf{Tentative Test Dates (7:00 p.m.) and Tentative Days Off:}
					\par  Test 1 - 16 February (Day Off: Friday, 04 March) 
					\par  Test 2 - 30 March (Day Off: Friday, 01 April) 
					\par  Test 3 - 27 April (Day Off: Friday, 29 April) \\
				\textbf{Tentative Online Quiz deadlines:} 11:59PM on below dates.
				Confirm and double check deadlines on Math 1205 syllabus and Math 1205
				homepage.  
					\par  Quiz 1 - Friday, 28 January
					\par  Quiz 2 - Wednesday, 02 February
					\par  Quiz 3 - Tuesday, 09 February
					\par  Quiz 4 - Wednesday, 23 February
					\par  Quiz 5 - Wednesday, 02 March
					\par  Quiz 6 - Wednesday, 16 March
					\par  Quiz 7 - Wednesday, 23 March
					\par  Quiz 8 - Tuesday, 29 March
					\par  Quiz 9 - Wednesday, 13 April
					\par  Quiz 10 - Wednesday, 20 April
					\par  Quiz 11 - Tuesday, 26 April \\
				\textbf{FINAL EXAM: Friday, 06 May; 7 PM - 9 PM} 
		
\end{document}
